Contextuality and Nonlocality in Discrete Quantum Theory

### 2016-01-29 DQC3.tex
"6.1 Gleason's Theorem in DQT" Updated....

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{amsfonts}
\usepackage{color}
\usepackage{stmaryrd}\usepackage{dsfont}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}		% customizable list environments
\newlength{\lyxlabelwidth}      % auxiliary length 
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\ifx\proof\undefined
\newenvironment{proof}[1][\protect\proofname]{\par
\normalfont\topsep6\p@\@plus6\p@\relax
\trivlist
\itemindent\parindent
\item[\hskip\labelsep\scshape #1]\ignorespaces
}{%
\endtrivlist\@endpefalse
}
\providecommand{\proofname}{Proof}
\fi
\theoremstyle{definition}
\newtheorem{problem}[thm]{Problem}

@@

For $d\ge3$, for any ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
if ${\cal P}$ is a state-function and probability, i.e.,
\begin{eqnarray}
 &  & \textrm{For any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}\textrm{ , }{\cal P}(\ket{i})={\cal P}(\gamma\ket{i})\textrm{ ,}\label{eq:parallel-DQT(I)-1}\\
 &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \sum_{i=0}^{d-1}{\cal P}\left(\ket{i}\right)=1}\textrm{ ,}\label{eq:total-probability-1}
\end{eqnarray}
there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.\footnote{In order to simplify the statement, we consider consider the probability
on the state vectors instead of the projectors or closed subspaces
as in the Gleason's original paper.}
\end{thm}
In contrast, when $d=2$, consider the discontinuous function ${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$
by 
\[
{\cal P}
\left(\begin{array}{c} \alpha_{0}\\ \alpha_{1} \end{array}\right)=
\cases{ 
1 & , if $\alpha_{0}\alpha_{1}>0$\\
\frac{1}{2} & , if $\alpha_{0}\alpha_{1}=0$\\
0 & , if $\alpha_{0}\alpha_{1}<0$ } 
\]
${\cal P}$ satisfies equation (\ref{eq:parallel-DQT(I)-1}) and (\ref{eq:total-probability-1})
because no matter the sign of $\alpha_{0}\alpha_{1}$, we always have
\[
{\cal P}\left(\begin{array}{c}
\alpha_{0}\\
\alpha_{1}
\end{array}\right)+{\cal P}\left(\begin{array}{c}
-\alpha_{1}\\
\alpha_{0}
\end{array}\right)=1\textrm{ .}
\]
However, ${\cal P}_{\rho}$ is always continuous. Therefore, we can
never find a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$.

An important meaning of Gleason's theorem is that the state space
is sufficient enough to produce every possible probability we get
from an experiment. Hence, we don't have to worry about whether there
is a chance that the probability got from a measurement cannot be
explained by a state, and we need to introduce a new state. This may
be analog to the fact that every algebraic equation over $\C$ can
be solved in $\C$ so that we don't have to introduce new numbers
to solve an equation. The other important meaning of Gleason's theorem
is that it implies the Born rule (\ref{prob1.eq-6})~\cite{peres1995quantum,inun.606849520040101}.
This is even more important for building a discrete quantum theory.
If we plug in vectors over $\ff{p^{2}}$ into the usual Born rule
(\ref{prob1.eq-6}), it gives an elements in $\ff{p}$ which has no
way interpreted as a probability. Hence, everyone who tried to build
a quantum theory over finite fields struggled on how to define a reasonable
probability. If Gleason's theorem works in any sense over finite fields,
we can have a reasonable way to induce the Born rule over finite fields.

A naive way to extend Gleason's Theorem in DQT may be as follow.
\begin{problem}
Given a state-function $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
which is also a probability, i.e., 
\begin{eqnarray}
 &  & \textrm{For any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ , }\hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ . }\label{eq:parallel-DQT}\\
 &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \bigvee_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}\textrm{possible . }\label{eq:total-probability-DQT}
\end{eqnarray}
Can we say something about $\hat{\pi}$?
\end{problem}
The answer is no, and the reasons are simple. First, compare the following
arithmetic equation and Boolean equation.
\begin{eqnarray}
p_{1}+p_{2}+p_{3} & = & 1\label{eq:arithmetic}\\
\pi_{1}\vee\pi_{2}\vee\pi_{3} & = & \text{possible}\label{eq:Boolean}
\end{eqnarray}
When $p_{1}=\frac{1}{2}$, we still have an equality $p_{2}+p_{3}=1$
for $p_{2}$ and $p_{3}$ because $\left(\mathbb{R},0,+\right)$ is
a group. In contrast, when $\pi_{1}=\text{possible}$, we know nothing
about $\pi_{2}$ and $\pi_{3}$ because $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$
is a semigroup without cancellative, i.e., $a\vee c=b\vee c$ does
not imply $a=b$. The difference between $\left(\mathbb{R},0,+\right)$
and $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$ suggests
us to study the range of the probability. A reasonable range should
have the structure $\left(\mathscr{L},0,1,\oplus,<\right)$, where
$\left(\mathscr{L},0,\oplus,<\right)$ is the underlying commutative
ordered semigroup~\cite{clifford1958} because the condition (\ref{eq:total-probability})
and (\ref{eq:total-probability-DQT}) suggests the value of the range
should be able to add together. $1\in\mathscr{L}$ is another special
value to indicate the total probability. For example, $\left(\mathscr{L}_{2},\text{impossible},\text{possible},\vee,<\right)$
and $\left(\mathbb{R},0,1,+,<\right)$ are two possible range of the
probability, but we cannot pick $\mathscr{L}=\ff{p^{2}}$ because
we cannot define an inequality such that $\left(\ff{p^{2}},0,+,<\right)$
be an ordered semigroup.

Second, Gleason's theorem relies a lot on the continuous probability~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.
However, continuity doesn't even make sense in DQT. This fact implies
that the structure of the domain of the probability, $\ffzd{p^{2}}$,
is also too weak. In order to think which structure we need, we can
check which the reasonable property ${\cal P}_{\Psi}:\C^{d*}\rightarrow\left[0,1\right]$
should have. Despite the total probability is one, ${\cal P}_{\Psi}$
must have 
\begin{eqnarray}
{\cal P}_{\Psi}\left(\ket{i}\right) & = & 0\textrm{ if }\ip{\Psi}{i}=0\label{prob1.eq-6-1}
\end{eqnarray}
where $\gamma\in\C^{*}$. Moreover, the probability must be invariant
under any rotation, i.e., 
\begin{equation}
{\cal P}_{U\Psi}\left(U\ket{i}\right)={\cal P}_{\Psi}\left(\ket{i}\right)\label{eq:rotation}
\end{equation}
for any unitary matrix $U$. Because we consider the probability of
two different state ${\cal P}_{\Psi}$ and ${\cal P}_{U\Psi}$ together,
it may be more reasonable to ask whether there is an unique ``Born
rule'' satisfying all the conditions, and our problem becomes
\begin{problem}
\label{prob:Gleason's}Is there a structure $\left(\mathscr{L},0,1,\oplus,<\right)$
such that $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\left(\ffzd{p^{2}}\rightarrow\left\{ x\in\mathscr{L}\middle|0\le x\le1\right\} \right)$
satisfying the following conditions is unique for $d\ge3$ and infinitely
many for $d=2$?\footnote{Instead of equation (\ref{enu:particular-vector-DQT(I)}), another
reasonable condition is $\braket{\Psi}{i}=0\Leftrightarrow\tilde{\pi}_{\Psi}\left(\ket{i}\right)=0$.
However, when the underlying group $\mathscr{L}=\mathscr{L}_{2}$,
this condition implies an unique solution for $d=2$. This is too
strong and is not what we want. } 
\begin{eqnarray}
 & \bullet & \textrm{For any orthonormal basis }\left\{ \ket{i}\right\} _{n=0}^{d-1}\subset\ffzd{p^{2}}\textrm{, }\label{enu:total-probability-DQT(I)}\\
 &  & \textrm{ \ensuremath{{\displaystyle \bigoplus_{i=0}^{d-1}\tilde{\pi}_{\Psi}\left(\ket{i}\right)=1}} .}\nonumber \\
 & \bullet & \textrm{If }\braket{\Psi}{i}=0\textrm{ ,}\textrm{then }\tilde{\pi}_{\Psi}\left(\ket{i}\right)=0\textrm{ .}\label{enu:particular-vector-DQT(I)}\\
 & \bullet & \textrm{For any vector }\ket{\Psi},\ket{i}\in\ffzd{p^{2}}\textrm{, }\nonumber \\
 &  & \textrm{and }U\textrm{ is a }d\textrm{-by-}d\textrm{ unitary matrix over }\ff{p^{2}}\textrm{, }\label{enu:unitary-DQT(I)}\\
 &  & \textrm{i.e. , }U^{\dagger}U=I\textrm{, then }\tilde{\pi}_{\Psi}(\ket{i})=\tilde{\pi}_{U\Psi}(U\ket{i})\textrm{. }\nonumber \\
 & \bullet & \textrm{For any vector }\ket{\Psi},\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{, }\nonumber \\
 &  & \tilde{\pi}_{\Psi}(\ket{i})=\tilde{\pi}_{\Psi}(\gamma\ket{i})\textrm{. }\label{enu:parallel-DQT(I)}
\end{eqnarray}

\end{problem}
The no-go theorem in section \ref{sub:A-No-Go-Theorem} said the if
$\left(\mathscr{L},0,1,\oplus,<\right)=\left(\mathbb{R},0,1,+,<\right)$,
there is no $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\ffzd{p^{2}}\rightarrow\mathscr{L}$
for $d\ge3$. It is easy to extend the no-go theorem and prove 
\begin{thm}
If $\left(\mathscr{L},0,\oplus,<\right)$ is a ordered group, then
there is no $\tilde{\pi}:\ffzd{p^{2}}\rightarrow\ffzd{p^{2}}\rightarrow\mathscr{L}$
satisfying all conditions in problem \ref{prob:Gleason's} for $d\ge3$.
\end{thm}
When we consider $\left(\mathscr{L}_{2},\text{impossible},\text{possible},\vee,<\right)$,
$\dpr$ defined in section \ref{sub:Interval-Valued-Probabilities-DQT}
satisfies all conditions, but $\dpr$ is not the unique solution because
of lack of cancellation law. It is still an open question whether
problem \ref{prob:Gleason's} is true or false in general.

\yutsung{Is that all probability value should be distinct be an reasonable
condition?}

%%%%%%%%%%%%%%%%%
\subsection {The Kochen-Specker Theorem in DQT}
The essence of the Kochen-Specker theorem is to ask if it is possible,
for a fixed $\ket{\Psi}\in\ffzd{p^{2}}$, to have another function
$v\left(\ket{\Phi}\right)$ playing the role of
$\dpr \left(\ket{\Psi},\ket{\Phi}\right)$ but failing to satisfy any
single one of the conditions in the set
(\ref{enu:total-probability-DQT(I)},\ref{enu:particular-vector-DQT(I)},
\ref{enu:parallel-DQT(I)},\ref{enu:unitary-DQT(I)}) and to show that
this cannot be true.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{amsfonts}
\usepackage{color}
\usepackage{stmaryrd}\usepackage{dsfont}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}		% customizable list environments
\newlength{\lyxlabelwidth}      % auxiliary length 
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\ifx\proof\undefined
\newenvironment{proof}[1][\protect\proofname]{\par
\normalfont\topsep6\p@\@plus6\p@\relax
\trivlist
\itemindent\parindent
\item[\hskip\labelsep\scshape #1]\ignorespaces
}{%
\endtrivlist\@endpefalse
}
\providecommand{\proofname}{Proof}
\fi
\def\casename{Case. }
 \newlist{casenv}{enumerate}{4}
 \setlist[casenv]{leftmargin=*,align=left,widest={iiii}}
 \setlist[casenv,1]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
 \setlist[casenv,2]{label={{\itshape\ \casename} \roman*.},ref=\roman*}
 \setlist[casenv,3]{label={{\itshape\ \casename\ \alph*.}},ref=\alph*}
 \setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}

@@

For $d\ge3$, for any ${\cal P}:\C^{d*}\rightarrow\left[0,1\right]$,
if ${\cal P}$ is a state-function and probability, i.e.,
\begin{eqnarray}
 &  & \textrm{For any vector }\ket{i}\in\C^{d*}\textrm{, and }\gamma\in\C^{*}\textrm{ , }{\cal P}(\ket{i})={\cal P}(\gamma\ket{i})\textrm{ ,}\label{eq:parallel-DQT(I)-1}\\
 &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \sum_{i=0}^{d-1}{\cal P}\left(\ket{i}\right)=1}\textrm{ ,}\label{eq:total-probability-1}
\end{eqnarray}
there is a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$~\cite{Redhead1987-REDINA,gleason1957,peres1995quantum}.\footnote{In order to simplify the statement, we consider consider the probability
on the state vectors instead of the projectors or closed subspaces
as in the Gleason's original paper.}
\end{thm}
In contrast, when $d=2$, consider ${\cal P}:\C^{2*}\rightarrow\left[0,1\right]$
such that if we restrict ${\cal P}$ on the real unit circle, we will
have a discontinuous function 
\[
{\cal P}
\left(\begin{array}{c} \cos\theta\\ \sin\theta \end{array}\right)=
\cases{ 
0 & , if $0 \le \theta < \frac{\pi}{2}$\\
1 & , if $\frac{\pi}{2} \le \theta < \pi$ } 
\]
${\cal P}$ satisfies equation (\ref{eq:parallel-DQT(I)-1}) and (\ref{eq:total-probability-1})
because we have 
\[
{\cal P}\left(\begin{array}{c}
\cos\theta\\
\sin\theta
\end{array}\right)+{\cal P}\left(\begin{array}{c}
-\sin\theta\\
\cos\theta
\end{array}\right)={\cal P}\left(\begin{array}{c}
\cos\theta\\
\sin\theta
\end{array}\right)+{\cal P}\left(\begin{array}{c}
\cos\left(\theta+\frac{\pi}{2}\right)\\
\sin\left(\theta+\frac{\pi}{2}\right)
\end{array}\right)=1\textrm{ .}
\]
However, ${\cal P}_{\rho}$ is always continuous. Therefore, we can
never find a density matrix $\rho$ such that ${\cal P}={\cal P}_{\rho}$.

Although the situation is different between $d=2$ and $d\ge3$ in
CQT, we may not identify a state from a probability in DQT no matter
the dimension of the system. In order to clearly state the theorem,
we define $\dpr_{\Psi}\left(\ket{i}\right)=\dpr\left(\ket{\Psi},\ket{i}\right)$.
Then, 
\begin{thm}
\label{thm:GleasonDQT}There exists $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}_{2}$
which is a state-function and a probability, i.e., 
\begin{eqnarray}
 &  & \textrm{For any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ , }\hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ . }\label{eq:parallel-DQT}\\
 &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \bigvee_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}\textrm{possible . }\label{eq:total-probability-DQT}
\end{eqnarray}
such that for any $\ket{\Psi}\in\ffzd{p^{2}},\dpr_{\Psi}\ne\hat{\pi}$.\end{thm}
\begin{proof}
Fix a basis $\{\ket{i}\}_{i=0}^{d-1}$. Consider 
\[
{\hat{\pi}}\left(\ket{\Phi}\right)=
\cases{ 
\textrm{impossible} & , if $\ip{\Phi}{0} = 0$ or $\ip{\Phi}{0} = \ldots = \ip{\Phi}{d-1}\ne 0$ ; \\
\textrm{possible} & , otherwise. } 
\]
It is easy to verify that equation (\ref{eq:parallel-DQT}) hold as
follow. 
\begin{eqnarray*}
 &  & \hat{\pi}\left(\ket{\Phi}\right)=\textrm{impossible}\\
 & \Leftrightarrow & \ip{\Phi}{0}=0\textrm{ or }\ip{\Phi}{0}=\ldots=\ip{\Phi}{d-1}\ne0\\
 & \Leftrightarrow & \gamma\ip{\Phi}{0}=0\textrm{ or }\gamma\ip{\Phi}{0}=\ldots=\gamma\ip{\Phi}{d-1}\ne0\\
 & \Leftrightarrow & \hat{\pi}\left(\gamma\ket{\Phi}\right)=\textrm{impossible}
\end{eqnarray*}
For equation (\ref{eq:total-probability-DQT}), because 
\[
\textrm{impossible}\lor\textrm{possible}=\textrm{possible ,}
\]
it is sufficient to prove for any $\ket{\Phi}\in\ffzd{p^{2}}$ such
that $\hat{\pi}\left(\ket{\Phi}\right)=\textrm{impossible}$, there
is a $\ket{\Psi}\in\ffzd{p^{2}}$ such that $\ip{\Phi}{\Psi}=0$ and
$\hat{\pi}\left(\ket{\Psi}\right)=\textrm{possible}$.
\begin{casenv}
\item When $\ip{\Phi}{0}=0$, $\ket{0}$ is what we want because $\ip{0}{0}=1\ne0$
implies $\hat{\pi}\left(\ket{0}\right)=\textrm{possible}$.
\item When $\ip{\Phi}{0}=\ldots=\ip{\Phi}{d-1}\ne0$, let $\alpha=\ip{\Phi}{0}$,
and consider the state 
\[
\ket{\Psi}=\left(\begin{array}{ccccc}
\alpha & -\alpha & 0 & \ldots & 0\end{array}\right)^{T}\textrm{ .}
\]
Then, $\ip{\Phi}{\Psi}=\alpha^{*}\alpha-\alpha^{*}\alpha=0$. Moreover,
$\ket{\Psi}{0}=\alpha^{*}\ne0$ and $\ket{\Psi}{0}=\alpha^{*}\ne-\alpha^{*}=\ket{\Psi}{1}$
implies $\hat{\pi}\left(\ket{\Psi}\right)=\textrm{possible}$.
\end{casenv}
Therefore, equation (\ref{eq:total-probability-DQT}) holds.

The last part of the theorem is to prove that for any $\ket{\Psi}\in\ffzd{p^{2}},\dpr_{\Psi}\ne\hat{\pi}$.
This part can be established by counting states. For any $\ket{\Psi}\in\ffzd{p^{2}}$,
\begin{eqnarray*}
 &  & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\dpr_{\Psi}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|\\
 & = & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\ip{\Psi}{i}=0\right\} \right|\\
 & < & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\hat{\pi}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|
\end{eqnarray*}
$\QED$
\end{proof}
There are reasons why there is no Gleason's theorem in DQT. First,
given ${\cal P}$ in CQT, we search for a mixed state $\rho$ such
that ${\cal P}={\cal P}_{\rho}$, but given $\hat{\pi}$ in DQT, we
only search for a pure state $\ket{\Psi}$ such that $\dpr_{\Psi}=\hat{\pi}$.
Notice that there are much more mixed states than pure states so that
it is likely we cannot find any pure state $\ket{\Psi}$ satisfying
$\dpr_{\Psi}=\hat{\pi}$ in DQT. Although this reason is important,
theorem \ref{thm:GleasonDQT} still hold even if we define a mixed
state. Assume $\rho$ is a mixed state between $\ket{\Psi_{1}}$ and
$\ket{\Psi_{2}}$, then we still have 
\begin{eqnarray*}
 &  & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\dpr_{\rho}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|\\
 & \le & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\dpr_{\Psi_{1}}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|\\
 & < & \left|\left\{ \ket{i}\in\ffzd{p^{2}}\middle|\hat{\pi}\left(\ket{i}\right)=\textrm{impossible}\right\} \right|
\end{eqnarray*}
Therefore, no matter how we define the mixed state, theorem \ref{thm:GleasonDQT}
still hold, and there are some other reasons why theorem \ref{thm:GleasonDQT}
hold.

Second, compare the following arithmetic equation and Boolean equation.
\begin{eqnarray}
{\cal P}\left(\ket{0}\right)+{\cal P}\left(\ket{1}\right)+{\cal P}\left(\ket{2}\right) & = & 1\label{eq:arithmetic}\\
\hat{\pi}\left(\ket{0}\right)\vee\hat{\pi}\left(\ket{1}\right)\vee\hat{\pi}\left(\ket{2}\right) & = & \text{possible}\label{eq:Boolean}
\end{eqnarray}
When ${\cal P}\left(\ket{0}\right)=\frac{1}{2}$, we still have an
equality ${\cal P}\left(\ket{1}\right)+{\cal P}\left(\ket{2}\right)=1$
for ${\cal P}\left(\ket{1}\right)$ and ${\cal P}\left(\ket{2}\right)$
because $\left(\mathbb{R},0,+\right)$ is a group. In contrast, when
$\hat{\pi}\left(\ket{0}\right)=\text{possible}$, we know nothing
about $\hat{\pi}\left(\ket{1}\right)$ and $\hat{\pi}\left(\ket{2}\right)$
because $\left(\mathscr{L}_{2},\text{impossible},\vee\right)$ is
a semigroup without cancellative, i.e., $a\vee c=b\vee c$ does not
imply $a=b$.

Third, even if we require the range of $\hat{\pi}$ has a group structure,
we still may not find $\dpr_{\Psi}=\hat{\pi}$.
%%%%%%%%%%%%%%%%%
\subsection {The Kochen-Specker Theorem in DQT}
The essence of the Kochen-Specker theorem is to ask if it is possible,
for a fixed $\ket{\Psi}\in\ffzd{p^{2}}$, to have another function
$v\left(\ket{\Phi}\right)$ playing the role of
$\dpr \left(\ket{\Psi},\ket{\Phi}\right)$ but failing to satisfy any
single one of the conditions in the set
(\ref{enu:total-probability-DQT(I)},\ref{enu:particular-vector-DQT(I)},
\ref{enu:parallel-DQT(I)},\ref{enu:unitary-DQT(I)}) and to show that
this cannot be true.
